Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-18 ms.tex
more plots :D
fixed latex syntax error
fixed major bug with new generations

$aS - bS^2$ is individuals becoming mature.\\
$\frac{cS}{1+eO}$ is searching individuals becoming occupiers through finding nests that are unoccuied.\\
$f$ is the metabolic death rate\.\
$g$ is the abandon rate.\\
$h$ is the rate at which occupiers die in a contest.\\

@@

$c_n$ is the stochatic reaction constant

>>>>

$aS - bS^2$ is individuals becoming mature.\\
$\frac{cS}{1+eO}$ is searching individuals becoming occupiers through finding nests that are unoccuied.\\
$f$ is the metabolic death rate.\\
$g$ is the abandon rate.\\
$h$ is the rate at which occupiers die in a contest.\\

@@

$c_n$ is the stochatic reaction constant\\
$c_n \cdot dt = $ the average probability that a particular combination of $R_n$, reactant molecules will react accordingly in the next infinitesimal time interval $dt$.
\citep{Gillespie-1976}

we generate the reactions then step through them with a population.
